Visualising metagenome differences

### 2023-11-21 analysis/metagenome.Rmd
Add more t-tests

@@

@@

>>>>

```{r}
genessplit |> filter(str_detect(gene, 'nifH') | str_detect(gene, 'acdS') | str_detect(gene, 'sctC')) |> 
  mutate(gene_class = case_when(str_detect(gene, 'nifH') ~ '*nifH*',
                                str_detect(gene, 'acdS') ~ '*acdS*',
                                str_detect(gene, 'sctC') ~ '*sctC*')) |>
  #group_by(Sample_species, Tissue, Sample_replicate, MAG) |> 
  #summarise(gene_class = paste0(sort(unique(gene_class)), collapse = ' & ')) |>
  group_by(Sample_species, Tissue, Sample_replicate) |> 
  count(gene_class) |> 
  mutate(Sample_species = trunc_str(Sample_species)) |> 
  mutate(Sample_species = paste0('*', Sample_species, '*')) |> 
  ggplot(aes(x=factor(Tissue, levels=rev(c('Shoot/Leaf', 'Shoot/Leaf Biofilm', 'Rhizome', 'Root'))), y=n, fill=Sample_species)) + 
  geom_boxplot(outlier.shape = NA) +
  facet_wrap(~factor(gene_class, levels=c('*acdS*', '*nifH*', '*sctC*')), scales = 'free_x') + 
  geom_point(position = position_jitterdodge(), aes(color=Sample_species)) +
  coord_flip() +
  theme_minimal() +
  labs(color='Species', fill='Species') +
  theme(axis.text.y =  element_markdown(),legend.text = element_markdown(),
        strip.text.x = element_markdown()) +
  ylab('Count of MAGs') + xlab('Species')
```
I like this one more. The differences are stronger.

# Statistic test

@@

First, a general one:

@@

## Subtests
Now let's make the specific ones; nifh, acdS, and sctC counts within Tissue=root across both species

### nifH
```{r}
tmp <- genessplit |> filter(str_detect(gene, 'nifH') & str_detect(Tissue, 'Root')) |> 
  mutate(gene_class = case_when(str_detect(gene, 'nifH') ~ 'nifH')) |> 
  group_by(Sample_species, Sample_replicate) |> count(gene_class) 
tmp  
```

```{r}
t.test(n ~ Sample_species, data=tmp)
```

P < 0.0005

### sctC

```{r}
tmp <- genessplit |> filter(str_detect(gene, 'sctC') & str_detect(Tissue, 'Root')) |> 
  mutate(gene_class = case_when(str_detect(gene, 'sctC') ~ 'sctC')) |> 
  group_by(Sample_species, Sample_replicate) |> count(gene_class) 
tmp  
```

```{r}
t.test(n ~ Sample_species, data=tmp)
```

p < 0.005

### acdS

```{r}
tmp <- genessplit |> filter(str_detect(gene, 'acdS') & str_detect(Tissue, 'Root')) |> 
  mutate(gene_class = case_when(str_detect(gene, 'acdS') ~ 'acdS')) |> 
  group_by(Sample_species, Sample_replicate) |> count(gene_class) 
tmp 
```

can't run t-test, only one group present!

```{r}
# t.test(n ~ Sample_species, data=tmp)
```
